Nanophotonic Computational Design

### 2013-03-16 paper/paper.tex
Draft done.

In order to design a broadband wavelength splitter,
    we modify our performance specification to include multiple target 
    wavelengths (with identical desired performance) around the 
    original target wavelengths, as seen in \fig{analysis_top}
    which reveals that broadband operation has been achieved.
The final result for the broadband wavelength splitter is shown in \fig{top_wdm}.
\myfig{analysis_top}
    {Broadband analysis of broadband wavelength splitter.
    The addition of multiple target wavelengths (vertical arrows)
    allows for 
    high-efficiency operation is achieved across a wide bandwidth.}
\myfig{top_wdm}
    {Broadband wavelength splitter final result.}
\myfig{analysis_temp_shift2}{}
\myfig{analysis_fab_shift2}{}
\myfig{top_wdm_overunder}{}

\section{Conclusion}
Conclusion

\end{document}

>>>>

In order to design a broadband wavelength splitter,
    we modify our performance specification to include multiple target 
    wavelengths (with identical desired performance) around the 
    original target wavelengths, as seen in \fig{analysis_top}
    which reveals that broadband operation has been achieved.
The final result for the broadband wavelength splitter is shown in \fig{top_wdm}.
\myfig{analysis_top}
    {Broadband analysis of broadband wavelength splitter.
    The addition of multiple target wavelengths (vertical arrows)
    allows for 
    high-efficiency operation is achieved across a wide bandwidth.}
\myfig{top_wdm}
    {Broadband wavelength splitter final result.
    The efficiencies at the central target wavelengths of 1550 nm and 1310 nm
    exceed those of its narrowband counterpart (\fig{spl_wdm}).}

\subsubsection{Temperature-robustness of broadband wavelength splitter}
We can now perform a temperature analysis of our broadband wavelength splitter,
    using $\Delta n_\text{Si} / \Delta T = 1.85 \cdot 10^{-4} K^{-1}$ 
    and $\Delta n_{\text{SiO}_2} / \Delta T = 0$ 
    (no refractive index shift for silica).
This analysis, shown in \fig{analysis_temp_shift2},
    reveals that stable operating points exist
    over a temperature range of nearly 1000 K.
Such a result is telling in that it demonstrates
    that on-chip optical devices can be designed to be \emph{passively} stable
    to temperature shifts which would typically be present in CPUs,
    since these are much less than 1000 K.
\myfig{analysis_temp_shift2}
    {Temperature analysis of the broadband wavelength splitter.
    Stable operating points (defined as efficiency $\ge$ 80\%)
    exist over a temperature shift of 905K.}

\subsubsection{Fabrication-robustness of broadband wavelength splitter}
A analysis with regard to fabrication-error
    was also performed on the broadband wavelength splitter.
The specific fabrication error was a general over- or under-etch
    of the device (input and output waveguides unaffected).
\Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching
    can be sustained before performance falls below 70\%, at the central
    operating wavelengths.
The structural variations at 8 nm of etch error are shown in \fig{top_wdm_overunder}.

\myfig{analysis_fab_shift2}
    {Analysis of fabrication-error on the performance of the broadband 
    wavelength splitter.
    Original central wavelengths are shown to hold greater than 70\% efficiency,
    in spite of up to 8 nm of over- or under-etch error.}
\myfig{top_wdm_overunder}
    {Comparison of under-etched, as-designed, and over-etched structures.
    Differences are subtle since the pixel size is 40 nm and the
    fabrication error is 8 nm.}

This result is significant in that it demonstrates
    that the design of broadband devices
    seems to be a valid heuristic in the search for 
    devices which are tolerant to temperature shifts and fabrication error.
Note, however, that our method, as formulated, is also able to
    deal with temperature and fabrication shifts explicitly as well;
    although such results are not demonstrated here.

\section{Conclusion}
We have developed and implemented a method to design linear nanophotonic structures
    which are fully three-dimensional and multi-modal,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
We demonstrate this capability by designing various nanophotonic mode converters,
    splitters, hubs, and fiber couplers.
Critically, many, if not all, of these devices have never been demonstrated before
    and are not able to be designed by hand.
In contrast, our method allows user to easily design such devices
    by virtue of our design-by-specification scheme.

In addition, we demonstrate the design of a broadband device 
    which is strongly robust to wavelength and temperature shift,
    as well as fabrication error.
We show that such a device has stable operating wavelengths 
    over temperature shifts as large as 905 K,
    or over-/under-etching error of up to 8 nm.
We suggest, based on this design, that wavelength tolerance
    may be a good heuristic to the design of temperature and fabrication-error
    tolerant nanophotonic devices.
\end{document}
